SBAT: A Simple Browser-based Annotation Tool with Interactive Visualization and Github Support

### 2024-09-01 paper/main.tex
update implementation

\begin{enumerate}
\item annotation ui from brat
The annotation user interface is made with the frontend UI component from Brat, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery. Moreover, to get rid of the dependancy on a server, all user actions such as creating, editing or deleting annotations are handled by the browser. This is realized by the LocalAjax class, which is written based on the LocalAjax function in brat-frontend-editor and is a local simulation of AJAX requests processing the data without actually sending real network requests. Other UI elements, such as the login buttons, are also implemented using HTML and Asynchronous JavaScript.
\item static web app hosted on github pages, no need of server, no server-side configuration, light-weighted
SBAT is a static web app that is hosted on github pages, and as there is no need of a server or any server-side configuration, anyone who have downloaded the repository can simply change the configurations and then host it on their own github pages. If it is not an annotation project which requires collaboration of many members, SBAT can also simply be used locally, by starting the index.js file in the local browser.
\item github API for reading and writing annotation files
SBAT uses Octokit, the official SDKs for the Github API.
octokit.js v4.0.2 [Computer software]. (2024). Retrieved from https://github.com/octokit/octokit.js
The user authentication through Github Personal Access Token enables creating a new user-authenticated Octokit object and obtaining information about branches and file content from the configured repository.  Likewise, creating a new commit and pushing to github repository is realized by first obtaining tree of all files from last commit, modifying the changed file or creating a new file, and the creating the new tree and commit with the octokit REST API endpoint.
\end{enumerate}

\section{Conclusion}
SBAT is an annotation tool that can be used to attach annotation labels to linguistic data. It is completely browser-based and only requires a browser to be executed. Furthermore, it can be combined well with github to import from and export annotations to user's own github repositories. It aims to provide a more simplified and no-server solution for annotation projects.\\

>>>>

\subsection{Annotation Interface}
SBAT's annotation interface is rooted in the frontend component from Brat, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery. On top of that, to remove the dependance on a server, all user actions such as creating, editing or deleting annotations are handled by the browser. This is realized by the LocalAjax class, adapting the LocalAjax function from brat-frontend-editor. It locally simulates AJAX requests to process the data without actually sending real network requests. Other UI elements, such as the login buttons, are also created by HTML and Asynchronous JavaScript. In this way, the complete user interface is embedded in a HTML webpage and all functions are locally executed in the browser.
\subsection{Browser-Based Construction}
As SBAT is a static web app without server communications, it can be hosted on Github Pages for free. But it is not mandatory to host the app in order to use it, as the index.js file can be used as an entry point to start the app locally in the browser. If the users want to access it online instead of locally, the source code can be directly uploaded to a Github repository to host a copy of SBAT on Github Pages. Moreover, to cater to different use cases, it is also easy to modify any part of the app -- SBAT uses ECMAScript Modules instead of CommonJS, so all modules are natively loaded in browser and no module bundler such as webpack is used. This allows direct modification of individual modules without the need of re-bundling.
\subsection{Usage of Github API}
SBAT uses Octokit \cite{octokit.js}, the official SDKs for the Github API, which enables the programmatical implementation of Github operations. The user authentication through Github Personal Access Token enables creating a new user-authenticated Octokit object and obtaining information about branches and file content from the configured repository. Likewise, creating a new commit and pushing to github repository is realized by first obtaining tree of all files from last commit, modifying the changed file or creating a new file, and the creating the new tree and commit it with the REST API endpoint of octokit.

\section{Conclusion}
SBAT is an annotation tool that can be used to attach labels to linguistic data. It is completely browser-based and only requires a browser to be executed. Furthermore, it can be combined well with github to import from and export annotations to user's own github repositories. It aims to provide a simpler and no-server solution for annotation projects.\\
